### 2018-11-27 Writing/draft_highlighted.tex
Updated formula + added note for similarity
awoonga

\noindent {\normalsize \sc Thomas Guillerme$^{1,2,*}$, and Martin D. Brazeau$^{2,3}$}\\
\noindent {\small \it 
$^1$School of Biological Sciences, University of Queensland, St. Lucia, Queensland, Australia.\\
$^2$Imperial College London, Silwood Park Campus, Department of Life Sciences, Buckhurst Road, Ascot SL5 7PY, United Kingdom.\\
$^3$Department of Earth Sciences, Natural History Museum, Cromwell Road, London, SW75BD, United Kingdom.\\}

@@

\subsubsection{Character Difference ($CD$)}
\begin{equation}
    CD_{(x,y)} = 1 - 2\left(\abs*{\frac{\sum_{i}^{n}\abs{x_{i} - y_{i}}}{n}-\frac{1}{2}}\right)
\end{equation}

@@

\section{Acknowledgements}
Calculations where done using the Imperial College London Cluster Services (doi: 10.14469/hpc/2232).
We thank Alberto Pascual Garcia for input in the design of the simulations protocol and Guillermo Herraiz Yebes and Abigail Pastore for helping with the CD metric proof and the \hl{three anonymous reviewers for there insightful comments}.

>>>>

\noindent {\normalsize \sc Thomas Guillerme$^{1,2,*}$, Abigail I. Pastore$^{1}$, and Martin D. Brazeau$^{2,3}$}\\
\noindent {\small \it 
$^1$School of Biological Sciences, University of Queensland, St. Lucia, Queensland, Australia.\\
$^2$Imperial College London, Silwood Park Campus, Department of Life Sciences, Buckhurst Road, Ascot SL5 7PY, United Kingdom.\\
$^3$Department of Earth Sciences, Natural History Museum, Cromwell Road, London, SW75BD, United Kingdom.\\}

@@

\subsubsection{Character Difference ($CD$)}
\begin{equation}
    CD_{(x,y)} = \abs*{\frac{\sum_{i}^{n}\abs{x_{i} - y_{i}}}{n-1}}
\end{equation}

%CD is similar to https://onlinelibrary.wiley.com/doi/full/10.1111/pala.12384 but by character rather than by species

@@

\section{Acknowledgements}
Calculations where done using the Imperial College London Cluster Services (doi: 10.14469/hpc/2232). @@@ plus awoonga
We thank Alberto Pascual Garcia for input in the design of the simulations protocol and Guillermo Herraiz Yebes and Abigail Pastore for helping with the CD metric proof and the \hl{three anonymous reviewers for there insightful comments}.
